A formalization of semi-simplicial and semi-cubical sets in dependent type theory

### 2023-01-17 paper/paper.tex
Progress
paper: introduce \DeltaHat

% Simplicial and Cubical sets
\newcommand{\DeltaPlus}{\ensuremath{\boldsymbol{\Delta}_+}}
\newcommand{\Cube}{\ensuremath{\boldsymbol{\square}}}
\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}

@@

While ordinary semi-simplicial sets are presheaves over the semi-simplex category $\hat{\Delta}$, augmented semi-simplicial sets are presheaves over, what we will define as, $\DeltaPlus$. There are different ways to define $\DeltaPlus$, upto equivalence, and we use a combinatorial definition. The reason for our choice is that this definition has a straightforward extension to semi-cubical sets.

>>>>

% Simplicial and Cubical sets
\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
\newcommand{\DeltaPlus}{\ensuremath{\boldsymbol{\Delta}_+}}
\newcommand{\Cube}{\ensuremath{\boldsymbol{\square}}}
\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}

@@

While ordinary semi-simplicial sets are presheaves over the semi-simplex category \DeltaHat, augmented semi-simplicial sets are presheaves over, what we will define as, \DeltaPlus. There are different ways to define \DeltaPlus, upto equivalence, and we use a combinatorial definition. The reason for our choice is that this definition has a straightforward extension to semi-cubical sets.
